Reanalysis Step 5: Outcome Analysis with Full Four-Treatment Interaction (Monotherapy Only)

### 2025-09-02 reanalysis-5-outcome_analysis-full_interaction.qmd
monotherapy ix

# Create a cross-tab to show the hierarchical effect
focal_assignment <- table(
  focal_laser = first_data$focal_laser_flag,
  assigned_treatment = first_data$treatment_type
)
log_message("Where focal laser patients were assigned:")
print(focal_assignment)
```

>>>>

# Create a cross-tab to show the hierarchical effect
focal_assignment <- table(
  focal_laser_flag = first_data$focal_laser_flag,
  assigned_treatment = first_data$treatment_type
)
log_message("Where focal laser patients were assigned:")
print(focal_assignment)
```
